### 2013-10-30 src2/thesis.tex
update

@@

@@

@@

Push arrays were invented by Koen Claessen and first implemented in Obsidian 
to provide more control over where computation takes place (which thread computes 
which element). Push arrays has since been experimented on by others and show up 
in Nikola~\citet{NIKOLAPUSH}, Feldspar and appear in StreamHS~\citet{FPCDSL}.

>>>>

\vspace{5mm} 
\emph{This section will be revised. I want to add more code examples.} 
\vspace{5mm}

@@

\emph{This list below will be revised. More details or code will be added.}

@@

\emph{This section will revised.}

@@

Push arrays were invented by Koen Claessen and first implemented in Obsidian 
to provide more control over where computation takes place (which thread computes 
which element). Push arrays has since been experimented on by others and show up 
in Nikola~\citet{NIKOLAPUSH} and Feldspar~\citet{FELDSPARPUSH}. Push arrays appear 
in StreamHS~\citet{FPCDSL} and in ~\citet{MOA} as part of a multi-dimensional array 
calculus in Standard ML.
